Equations & R Code

### 2017-03-11 manuscript/coexistence-stability_ms.Rmd
more writing; adding conclusions and limitations section

>>>>

LIMITATIONS AND CONCLUSIONS
---------------------------
\new{What we have presented here is clearly just a beginning.
Theoretical explorations of the diversity--ecosystem variability relationship over the past three decades have highlighted numerous context-dependent processes that determine how much diversity can buffer ecosystem variability, and we have added another wrinkle.
To make our current analysis tractable, we ignored several potentially important processes and phenomena.
For example, we assumed all species pairs have the same environmental response correlations (e.g., $\rho_{ij} = \rho$), which is clearly not true in nature and can mediate the impact of dominant species on ecosystem variability} [@Thibaut2013].
\new{We also limited our analysis to four-species communities so we could easily compare the storage effect and relative nonlinearity.
Although our initial results suggest more species rich communities continue to buffer ecosystem variability under the storage effect (Fig. S1-x), future research should focus specifically on the storage effect to elaborate on our initial findings.
Lastly, we ignored demographic stochasticity, assuming our species had a generous seed source to bounce back from low population density.
But this need not be the case, and increasing environmental variability may threaten small populations even as it promotes coexistence of new species.
This dynamic may be especially relevant to applied work because habitat fragmentation and increasing environmental variability are likely to happen together.}

\new{Perhaps most important will be linking our results from a specific mechanistic model to more general quantitative frameworks.
Using a very general model,} @Thibaut2013 \new{show that positive diversity--ecosystem variability relationships are possible.
Specifically, ...}

### 2017-03-11 manuscript/coexistence-stability_ms.tex
more writing; adding conclusions and limitations section

@@

>>>>

\subsection{LIMITATIONS AND
CONCLUSIONS}\label{limitations-and-conclusions}

\new{What we have presented here is clearly just a beginning.
Theoretical explorations of the diversity--ecosystem variability relationship over the past three decades have highlighted numerous context-dependent processes that determine how much diversity can buffer ecosystem variability, and we have added another wrinkle.
To make our current analysis tractable, we ignored several potentially important processes and phenomena.
For example, we assumed all species pairs have the same environmental response correlations (e.g., $\rho_{ij} = \rho$), which is clearly not true in nature and can mediate the impact of dominant species on ecosystem variability}
(Thibaut \& Connolly 2013).
\new{We also limited our analysis to four-species communities so we could easily compare the storage effect and relative nonlinearity.
Although our initial results suggest more species rich communities continue to buffer ecosystem variability under the storage effect (Fig. S1-x), future research should focus specifically on the storage effect to elaborate on our initial findings.
Lastly, we ignored demographic stochasticity, assuming our species had a generous seed source to bounce back from low population density.
But this need not be the case, and increasing environmental variability may threaten small populations even as it promotes coexistence of new species.
This dynamic may be especially relevant to applied work because habitat fragmentation and increasing environmental variability are likely to happen together.}

\new{Perhaps most important will be linking our results from a specific mechanistic model to more general quantitative frameworks.
Using a very general model,} Thibaut \& Connolly (2013)
\new{show that positive diversity--ecosystem variability relationships are possible.
Specifically, ...}

@@

\hypertarget{ref-Thibaut2013}{}
Thibaut, L.M. \& Connolly, S.R. (2013). Understanding
diversity-stability relationships: Towards a unified model of portfolio
effects. \emph{Ecology Letters}, 16, 140--150.
